%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\documentclass{article}

\usepackage{amsfonts}
\usepackage{amsmath}
\usepackage{amssymb}
\usepackage{bm}
\usepackage{dcolumn}
\usepackage{graphicx}
\usepackage{graphics}
\usepackage[latin1]{inputenc}
\usepackage{latexsym}
\usepackage{rotating}
\usepackage{url}
\usepackage{xspace}
\usepackage[usenames]{color}
\usepackage{mathrsfs}
\usepackage{hyperref}
\usepackage{epstopdf}
\usepackage{verbatim}
\usepackage{authblk}
\usepackage{tensor}
\usepackage[margin=1.0in]{geometry}
\usepackage[scientific-notation=true]{siunitx}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\newcommand{\be}{\begin{equation}}
\newcommand{\ee}{\end{equation}}
\newcommand{\bal}{\begin{align}}
%\end{align} command not allowed by LaTex syntax
\newcommand{\bsp}{\begin{split}}
\newcommand{\esp}{\end{split}}

\newcommand{\GR}{{\mbox{\tiny GR}}}
\newcommand{\Hz}{{\mbox{\tiny H}}}
\newcommand{\new}{{\mbox{\tiny new}}}
\newcommand{\old}{{\mbox{\tiny old}}}
\newcommand{\eff}{{\mbox{\tiny eff}}}
\newcommand{\nonlin}{{\mbox{\tiny nonlin}}}
\newcommand{\ISCO}{{\mbox{\tiny ISCO}}}
\newcommand{\LR}{{\mbox{\tiny LR}}}

\newcommand{\bw}{\begin{widetext}}
\newcommand{\ew}{\end{widetext}}

\newcommand{\nn}{\nonumber}
\newcommand{\ph}{\phantom{n}}
\newcommand{\pd}{\partial}
\newcommand{\cd}{\nabla}
\newcommand{\tn}{\tensor}
\newcommand{\tnst}{\tensor*}

\newcommand{\ssqth}{\sin^2{\theta}}
\newcommand{\csqth}{\cos^2{\theta}}

\newcommand{\ext}{\mathrm{ext}}
\newcommand{\inter}{\mathrm{int}}
\newcommand{\mcl}{\mathcal}

\newcommand{\mrm}{\mathrm}
\newcommand{\rarr}{\rightarrow}
\newcommand{\larr}{\leftarrow}

\newcommand{\lb}{\left(}
\newcommand{\rb}{\right)}
\newcommand{\lcb}{\left\{}
\newcommand{\rcb}{\right\}}
\newcommand{\lsb}{\left[}
\newcommand{\rsb}{\right]}
\newcommand{\ld}{\left.}
\newcommand{\rd}{\right.}

\newcommand{\red}[1]{\textcolor{red}{#1}}
\newcommand{\as}[1]{\textcolor{cyan}{#1}}
\newcommand{\blue}[1]{\textcolor{blue}{#1}}
\newcommand{\ny}[1]{\textcolor{blue}{\it{\textbf{ny: #1}}}\xspace}

\newcommand{\efun}{\mathrm{(exp)}}
\newcommand{\lin}{\mathrm{(lin)}}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{document}
\title{eXtreme Partial Differential Equation Solver}

\author{Andrew Sullivan}
\affil{Department of Physics, Montana State University, Bozeman, MT 59717, USA.}

\date{\today}

\maketitle

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

This is the documentation of the eXtreme Partial Differential Equation Solver (XPDES) as detailed
in arxiv:TBD. This includes an overview of each component and the necessary steps to compile and
execute the program. For any questions, contact Andrew Sullivan at andrew.sullivan4@montana.edu.

\section{Folder Structure}
\label{sec:folderstruct}

The XPDES project folder is structured as such:

\begin{itemize}
\item Code
\begin{itemize}
\item BVP\_GENICBC.c: procedurally generated C-file to evaluate boundary conditions at each iteration and set initial guess.
\item BVP\_GENsys.c: procedurally generated C-file to evaluate residual and Jacobian at each iteration.
\item BVP\_grid.c: Grid adjustment and interpolation.
\item BVP\_header.h: Main header file. Provides every BVP function declaration as well as `\#include' the procedurally generated field equation and Jacobian function declarations.
\item BVP\_LSsolver.c: Modular linear system solver.
\item BVP\_main.c: Main Newton-Raphson control loop.
\item BVP\_out.c: Output generator to directory `Data/BVPout'.
\item BVP.c: Main file to initialize executable variables and call `BVP\_main()'.
\end{itemize}
\item Documentation
\begin{itemize}
\item MasterDoc.pdf: Master documentation file
\item Linear Solvers.pdf: Description of linear solver algorithms
\end{itemize}
\item Execs
\begin{itemize}
\item BVPEDGB.exe: Main executable for scalar-Gauss-Bonnet gravity.
\item mgen.exe: Executable to generate C header function declarations and Maple field equation exporter code.
\item ibgen.exe: Executable to generate initial and boundary conditions.
\item jgen.exe: Executable to generate system Jacobian.
\end{itemize}
\item Funcs
\begin{itemize}
\item CExport\_Funcs.c: C file with procedurally generated function declarations that is \#included in the C header file.
\item FEout.c: C file with exported field equations for evaluation.
\item ICBCout.c: C file with exported initial conditions and boundary conditions for evaluation.
\end{itemize}
\item Gens
\begin{itemize}
\item Maple\_Export Folder
\begin{itemize}
\item This folder contains the Maple field equation calculation and export. Filenames have the general structure ``FE\_THEORY\_export.mw". Creates: `FEout.c'.
\end{itemize}
\item Export\_MapleGen.c: C code to generate C header function declarations and Maple field equation exporter code. Creates: `Decl\_JSFuncs.c', `Decl\_CFuncs.c', `MapleREAD\_FEexport.txt', and `MapleREAD\_ICBCexport.txt'.
\item Export\_ICBC.c: C code to generate C initial conditions and boundary conditions. Creates: `BVP\_ICBC.c'.
\item Export\_Jac.c: Code to procedurally generate the system Jacobian evaluation file. Creates: `BVP\_sys.c'.
\item MapleREAD\_FEexport.txt: Text file with Maple commands to calculate and export the field equations. Executed through a ``read" command in the Maple command line.
\item MapleREAD\_ICBCexport.txt: Text file with Maple commands to calculate and export initial conditions and boundary conditions. Executed through a ``read" command in the Maple command line.
\end{itemize}
\item BVPcompile.sh: Bash compile file
\item BVPbatch.sh: Bash executable file
\end{itemize}



%----------------------------------------
\subsection{Compilation Pipeline}
\label{ssec:exec}

To facilitate the variable system of equations, certain files must be procedurally generated to adjust for the number of equations and unknown functions. This requires some back and forth communication between C executables and Maple. Reprocedurally generating all of the C-files is unnecessary as you can simply use the pre-generated files that will be described in the next subsection. For completeness, the step by step process is all done from the terminal using `BVPcompileFULL.sh':

\begin{enumerate}
\item Compile full program with `BVPcompileFULL.sh'
\begin{enumerate}
\item The generators must be compiled with the user defined input of the number of field equations `nfields' which will be twice the number of fields. For example, for scalar-Gauss-Bonnet gravity, the 4 metric functions and the scalar field provide 5 fields total, each with a mixed partial derivative field equation associated with it for a total of 10 field equations so $\mathrm{nfields} = 10$. The maximum derivative order must also be supplied.
\begin{itemize}
\item `Export\_MapleGen.c' $\rarr$ `mgen.exe'
\end{itemize}
\item Generators are executed
\begin{itemize}
\item `mgen.exe' procedurally generates $\rarr$ `MapleREAD\_FEexport.txt' and `MapleREAD\_ICBCexport.txt' as well as `Decl\_JSFuncs.c' and `Decl\_CFuncs.c'. These are essential as the number of arguments to every declared function will vary depending on the number of field equations.
\begin{itemize}
\item `MapleREAD\_FEexport.txt' and `MapleREAD\_ICBCexport.txt' are read inside Maple to calculate and export the field equations and the initial and boundary conditions.
\item `Decl\_JSFuncs.c' provides the function declarations for the estimation of the number of nonzeros of the Jacobian. They are `\#included' into the `BVP\_header.h' file.
\item `Decl\_CFuncs.c' provides the function declarations for the Newton polynomial calculator `NP\_calc.c' (which needs the maximum derivative order), the physical observables, the field equation residuals, the Jacobian partial derivatives, the boundary conditions, and the initial conditions. They are `\#included' into the `BVP\_header.h' file.
\end{itemize}
\end{itemize}
\item On the pause prompt...
\end{enumerate}
\item Execute the Maple worksheet in the Maple\_Export folder.
\begin{enumerate}
\item Maple will ``read" `MapleREAD\_FEexecute.txt' and procedurally generate $\rarr$ `Defn\_FEout.c'. These are the function declarations for the declared functions above.
\item Maple will ``read" `MapleREAD\_ICBCexecute.txt' and procedurally generate $\rarr$ `Defn\_ICBCout.c'. These are the function declarations for the declared functions above.
\end{enumerate}
\item Press enter terminal window to continue compiling the full program through gcc $\rarr$ `BVPNAME.exe'
\begin{itemize}
\item Automatically, `Export\_NNZGen.c' is compiled into `nnzgen.exe' which uses the defined Jacobian structure functions from `Decl\_JSFuncs.c' and `Defn\_JSFuncs.c' to estimate the number of the nonzeros of the Jacobian when given a grid size so that the algorithm can calculate approximately how much memory to allocate.
\item Automatically, `Export\_CGen.c' uses `CodeGen\_GENNNZ.c' and is compiled into `cgen.exe' which procedurally generates the intial conditions, boundary conditions, and Jacobian evaluation C-files in the `Code' folder. `BVP\_GENICBC.c' and `BVP\_GENsys.c' respectively.
\item Then `BVPNAME.exe' is compiled to the `Execs' folder.
\end{itemize}
\item Execute program with `BVPbatch.sh' to determine inputs. WARNING: this will also delete and remake the `Data' directory where the solutions are stored.
\end{enumerate}




%----------------------------------------
\subsection{Compilation Shortcut}
\label{ssec:short}

The field equation dependent files that are required upon compilation are:
\begin{itemize}
\item `/Code/BVP\_GENICBC.c'
\item `/Code/BVP\_GENsys.c'
\item `/Funcs/Decl\_CFuncs.c'
\item `/Funcs/Decl\_JSFuncs.c'
\item `/Funcs/Defn\_FEout.c'
\item `/Funcs/Defn\_ICBCout.c'
\item `/Funcs/Defn\_JSout.c'
\end{itemize}

To compile, copy the above files from the labeled folder in the `XPDES' directory into their respective location (either `/Code' or `/Funcs') and from the command line execute `BVPcompile.sh. This will compile and place the `BVPNAME.exe' executable in the `/Execs' folder.




%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\end{document}

